Data Dashboard

### 2020-07-22 analysis/05_market_simulator.Rmd
updated public_political_social_charity_demo beta
changed beta's for plotly to public_political_social_charity_demo

##### Updated the beta's to be just the betas from the public_political_social_chartiy_demo Thetas

beta <- public_political_social_charity_demo

@@

df <- reactive({
  #Amnesty International
    beta$ai_value <- 0
    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_noncentered[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_noncentered[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_noncentered[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_noncentered[,2])),2)

@@

  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  df <- as.data.frame(matrix(data, 8, 1))
  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  colnames(df) <- c('Value', 'Organization', "Type")

@@

```{r}
renderValueBox({
  choice = df()
  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(intercept_noncentered[,2])),2)
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_noncentered[,2])),2)
  valueBox(gp_exp_util,
           color = "#3fad48")
})
```

>>>>

##### Updated the beta's to be just the betas from the public_political_social_charity_demo Thetas

beta <- as.data.frame(matrix(rep(0), nrow = 13))

@@

df <- reactive({
  #Amnesty International
  beta$ai_
  value <- 0
    beta$ai_value[beta$levels == 'Amnesty International'] <- 1
    beta$ai_value[beta$levels %in% input$ai_issue] <- 1
    beta$ai_value[beta$levels %in% input$ai_fin_trans] <- 1
    beta$ai_value[beta$levels %in% input$ai_account] <- 1
    beta$ai_value[beta$levels %in% input$ai_funding] <- 1
    beta$ai_value[beta$levels %in% input$ai_gov_relat] <- 1
  #Greenpeace
    beta$gp_value <- 0
    beta$gp_value[beta$levels == 'Greenpeace'] <- 1
    beta$gp_value[beta$levels %in% input$gp_issue] <- 1
    beta$gp_value[beta$levels %in% input$gp_fin_trans] <- 1
    beta$gp_value[beta$levels %in% input$gp_account] <- 1
    beta$gp_value[beta$levels %in% input$gp_funding] <- 1
    beta$gp_value[beta$levels %in% input$gp_gov_relat] <- 1
  #Oxfam
    beta$ox_value <- 0
    beta$ox_value[beta$levels == 'Oxfam'] <- 1
    beta$ox_value[beta$levels %in% input$ox_issue] <- 1
    beta$ox_value[beta$levels %in% input$ox_fin_trans] <- 1
    beta$ox_value[beta$levels %in% input$ox_account] <- 1
    beta$ox_value[beta$levels %in% input$ox_funding] <- 1
    beta$ox_value[beta$levels %in% input$ox_gov_relat] <- 1
  #Redcross
    beta$rc_value <- 0
    beta$rc_value[beta$levels == 'Red Cross'] <- 1
    beta$rc_value[beta$levels %in% input$rc_issue] <- 1
    beta$rc_value[beta$levels %in% input$rc_fin_trans] <- 1
    beta$rc_value[beta$levels %in% input$rc_account] <- 1
    beta$rc_value[beta$levels %in% input$rc_funding] <- 1
    beta$rc_value[beta$levels %in% input$rc_gov_relat] <- 1
    beta

@@

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)

@@

  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  df <- as.data.frame(matrix(data, 8, 1))

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  colnames(df) <- c('Value', 'Organization', "Type")

@@

```{r}
renderValueBox({
  choice = df()
  ai_exp_util <- round(exp(t(choice[,3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  valueBox(ai_exp_util,
           color = "#FFC30B")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  valueBox(gp_exp_util,
           color = "#3fad48")
})
```
